Colonies - Compute Continuums across Platforms

### 2023-04-05 paper_2023/paper.tex
wip

Built on a modular microservice architecture, Colonies effectively decomposes complex workflows into highly composable functions. With the use of an HTTP protocol, these composable functions can be implemented in any computer language, and be executed by independent executors deployed across various systems, e.g. cloud, edge, high-performance computing (HPC) environments, devices, or even web browsers. By using a zero-trust security protocol, a collection of distributed executors can function as a single cohesive unit, thereby establishing seamless compute continuums across multiple platforms.

@@

This paper presents a framework called Colonies, specifically designed to implement a distributed virtual computer system. Colonies is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment. The primary objective is to establish a platform where monolithic workflows can be decomposed into independent computational units that can easily integrate with other systems or applications. These compute units can be implemented in any computer language and be deployed anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems.

\section{Related work}
Workflow management has been extensively studied in both academic and industrial settings with numerous approaches \cite{service_wfs, schmitt2022workflow, GarciaRepresa1740746, Ouyang2010, NIKOLOV2021100440, workflow_in_bigdata} proposed to address the challenges in this field. Recently, Apache Airflow \cite{apache_airflow} has become a popular open-source workflow management system for handling data engineering pipelines. Like Colonies, Apache Airflow enables developers to create custom operators and executors that can be integrated with various systems. Additionally, Apache Airflow offers an HTTP API that makes it possible to develop software development kits (SDKs) in various programming languages. However, Apache Airflow does not realy on a queuing system. Instead, it must be integrated with a message broker, such as RabbitMQ \cite{rabbitmq} or Kafka \cite{apache_kafka}, to implement task queues, resulting in a more complex architecture than Colonies. Furthermore, Colonies is based on a distributed microservice architecture that makes it more suitable for DevOps software development. As Colonies is loosely coupled, executors can be implemented and dynamically deployed without reconfiguring the workflow engine, effectively turning it to a grid computing platform.

@@

J. Represa et al. \cite{GarciaRepresa1740746} explore various challenges associated with developing microservice-based workflow management for industrial automation within the context of the Arrowhead project. The authors conclude that microservice-based workflow technologies is viable for industrial applications, particularly due to their inherent flexibility. The primary contribution of this paper is a comprehensive technical description of how to implement a distributed workflow engine based on microservice principles, extending beyond orchestrating microservices to execute automation tasks within one platform. The vision is to create a distributed architecuture, where microservices can reside anywhere on the Internet and still function as a cohesive unit to execute cross-platform workflows.

Grid computing is a distributed computing model that allows multiple computers, sometimes geographically distributed, to work together to solve large-scale computational problems. It can be used to harness compute resources from numerous computers to solve complex tasks. To the authors best knowledge, no one has ever used to grid platform as an integration platform to orchestrate AI workload across platforms. The main contribution of this paper is a technical description of the Colonies framework and a description of potential use cases.

>>>>

Built upon a modular microservice architecture, Colonies enables complex workflows to be broken down into composable functions. With the use of an HTTP protocol, these composable functions can be implemented in any programming language and be executed by independent executors deployed across various platforms on the Internet, such as cloud, edge, high-performance computing (HPC) environments, devices, or even web browsers. With the integration of a zero-trust security protocol, a collection of distributed executors can operate as a unified entity, thus establishing seamless computational continuums across multiple platforms.

@@

This paper presents a framework called Colonies, specifically designed to implement a \emph{distributed virtual computer system} that can integrate any third-party system. Colonies is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment. The primary objective is to establish a platform where monolithic workflows can be decomposed into independent computational units that can easily integrate with other systems or applications. These compute units can be implemented in any computer language and be deployed anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems.

\section{Related work}
Workflow management has been extensively studied in both academic and industrial settings with numerous approaches \cite{service_wfs, schmitt2022workflow, GarciaRepresa1740746, Ouyang2010, NIKOLOV2021100440, workflow_in_bigdata} proposed to address the challenges in this field. Recently, Apache Airflow \cite{apache_airflow} has become a popular open-source workflow management system for handling data engineering pipelines. Like Colonies, Apache Airflow enables developers to create custom operators and executors that can be integrated with various systems. Additionally, Apache Airflow offers an HTTP API that makes it possible to develop software development kits (SDKs) in various programming languages. However, Apache Airflow does not realy on a queuing system. Instead, it must be integrated with a message broker, such as RabbitMQ \cite{rabbitmq} or Kafka \cite{apache_kafka}, to implement task queues, resulting in a more complex architecture than Colonies. Furthermore, Colonies is based on a distributed microservice architecture that makes it more suitable for DevOps software development. As Colonies is loosely coupled, executors can be implemented and dynamically deployed without reconfiguring the workflow engine.

@@

J. Represa et al. \cite{GarciaRepresa1740746, GarciaRepresa1640771} explore various challenges associated with developing microservice-based workflow management for industrial automation within the context of the Arrowhead project \cite{delsing2017iot}. The authors conclude that microservice-based workflow technologies is viable for industrial applications, particularly due to their inherent flexibility. The primary contribution of this paper is a comprehensive technical description of how to implement a distributed workflow engine based on microservice principles, extending beyond orchestrating microservices to execute automation tasks within one platform. The vision is to create a distributed architecuture, where microservices can reside anywhere on the Internet and still function as a cohesive unit to execute cross-platform workflows.

Grid computing \cite{grid_computing} is a distributed computing model that allows multiple computers, which may be geographically dispersed, to collaborate in addressing large-scale computational challenges. The Colonies framework is founded upon a grid computing model, with the primary purpose of assigning tasks to distributed executors. To the best of the authors' knowledge, no previous work has integrated a microservice-oriented architecture with a grid computing model to serve as an integration point for coordinating artificial intelligence workloads across a diverse range of platforms. Additionally, Colonies is designed to function as a ledger, offering complete transparency and execution history, which is essential for implementing zero-trust security.

\begin{figure}[h]
	\centering
    \includegraphics[scale=0.35]{overview.png}
	\caption{Overview of ....}
	\label{fig:function_spec}
\end{figure}
